---
title: "Reletório do AR"
author: "R"
date: "March 5, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Relatório 1

### Description

Daily air quality measurements in New York, May to September 1973.




### Base de dados
```{r , echo=FALSE}
library(datasets)
base <- airquality

head( base , 10)

```



Daily readings of the following air quality values for May 1, 1973 (a Tuesday) to September 30, 1973.

Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island

Solar.R: Solar radiation in Langleys in the frequency band 4000–7700 Angstroms from 0800 to 1200 hours at Central Park

Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport

Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.


A base possui **`r dim(base)[1] `** observações e **`r dim(base)[2] `** variáveis.


```{r}

summary(base)

```


```{r}
dadosValidos <- complete.cases(base) 

base <- base[dadosValidos , ]


```


```{r}

summary(base)

```

```{r}
#write.csv( base , "base_airquality_limpo.csv" )
```

```{r}
#View(base)
```

```{r}
mes5 <- base$Month == 5
dados_mes5 <- base[mes5 , ]

plot( dados_mes5$Day , dados_mes5$Temp)

```

```{r}

library(ggplot2)

ggplot( dados_mes5 , aes( x= Day , y = Temp )  ) + geom_point() + geom_line()

```

```{r}


ggplot( base , aes( x= Day , y = Temp, colour = factor(Month) )  ) + geom_point() + geom_line()

```

```{r}

ggplot( base , aes( x= Day , y = Temp, colour = factor(Month) )  ) + geom_point() + geom_line() + facet_grid( Month ~ . )
```

```{r}
ggplot( base , aes( x= Day , y = Temp, colour = factor(Month) )  ) + geom_point() + geom_line() + facet_grid( . ~ Month )
```


```{r}
ggplot( base , aes( x= Day , y = Temp, colour = factor(Month) )  ) + geom_point() + geom_line() + facet_grid( . ~ Month )
```



```{r}
g <- ggplot( base , aes( x= Day , y = Temp, colour = factor(Month) )  ) 

g + geom_point() + facet_grid( . ~ Month ) + geom_smooth() + labs(title = "Temperatura por dia") + xlab("Dia") + ylab("Temperatura")

```



```{r}

mediaTemp <- mean(base$Temp)

ggplot( base , aes( x= Day , y = Temp, colour = factor(Month) )  ) + geom_point() + geom_line() + facet_grid( . ~ Month ) + geom_hline(yintercept = mediaTemp)
```


