---
title: "Titanic"
author: "R"
date: "March 5, 2017"
output: html_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sobreviventes

pclass: A proxy for socio-economic status (SES)
1st = Upper
2nd = Middle
3rd = Lower

age: Age is fractional if less than 1. If the age is estimated, is it in the form of xx.5

sibsp: The dataset defines family relations in this way...
Sibling = brother, sister, stepbrother, stepsister
Spouse = husband, wife (mistresses and fiancés were ignored)

parch: The dataset defines family relations in this way...
Parent = mother, father
Child = daughter, son, stepdaughter, stepson
Some children travelled only with a nanny, therefore parch=0 for them.

```{r}

library(dplyr)
library(ggplot2)
library(readr)


base <- read_csv("base/train.csv")

#rm( train)
head( base)
#View(base)

summary(base)

```


```{r}
dim(base)

mediaIdade <- mean(base$Age , na.rm = TRUE)

sort(table((base$Age)))



summary(base$Age)

table(base$SibSp)
table( base$Sex)


criancas <- base$Age < 16
base1 <- base[criancas, ]
base1 <- base1[complete.cases(base1) , ]


dim(base1)
sum( base1$Survived )



```

```{r}

resumo <- base %>% group_by(Sex , Survived) %>%summarise( total = n()    )

resumo

ggplot(resumo , aes( Sex , total ,col= factor(Survived) ) ) +
        geom_bar(stat = "identity" )


ggplot(resumo , aes( Sex , total ,fill= factor(Survived) ) ) +
        geom_bar(stat = "identity" )

```



```{r}
baseClasse <- base %>% 
        filter( Survived == 1 ) %>%
        group_by(Pclass)%>%
        summarise( total = n() )

ggplot(baseClasse , aes( Pclass , total) ) + geom_bar(stat = "identity")
```


